\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Bang Nguyen}

\section{Work experience}

\begin{eventlist}

\item{October 2017 -- Present}
    {DiUS, Sydney}
    {Senior Developer}

    Working as a consultant on wide range of projects and technology. The projects
    I have worked on involve but not limit to belows
    \newline- Discuss the architecture of the application
    \newline- Develop highly available and fault tolerant system that can handle burst-able data being sent 24/7 using a TCP-based protocol
    \newline- Develop a chatbot to automate tasks which previously handle by human in call center
    \newline- Break monolithic application in to smaller microservices
    \newline- Develop and maintain backend APIs

\item{September 2015 -- September 2017}
    {DIGIVIZER, Sydney}
    {Ruby Developer}

Develop social analytics platform which allows users to discover
what matter to them on social platforms (Twitter, Facebook, Instagram).
This could help business owners find a relevant customers
to their business and provide them with insight analytics.

\item{September 2014 -- September 2015}
    {GET UP!, Sydney}
    {Fullstack Software Developer}

Develop and maintain Tijuana Framework which is a CMS
used by campaigners to blast out emails to GetUp's members.
Work in all layers of application stack from cloud infrastructure
to database to application code to user interface.

\item{July 2013 -- April 2014}
    {SIMPSON STRONGTIE, Vietnam}
    {Technical Leader}

Design, develop and maintain applications to automate works which were previously done by construction engineers.
Design, develop and test new features of Component Solutions Suite to gather all scattered databases to one centric database.
Manage team and provide estimation to development tasks.

\item{September 2012 -- June 2013}
    {GLOBAL CYBERSOFT, Vietnam}
    {Lead Engineer}

Develop and maintain Set Up Box's applications.
Provide solutions to improve Set Up Box's performance.

\item{September 2009 -- October 2010}
    {FPT SOFTWARE, Vietnam -- WAE, Vietnam}
    {Mobile Developer}

Maintain Windows Phone mobile applications.
\newline Design, develop and maintain Android game named Cubic Gomoku.
\newline Design, develop Youtube-like program using Youtube's API.

\item{April 2008 -- August 2009}
    {RENESAS Design, Vietnam}
    {Embedded Software Engineer}

Develop and maintain aacPlus decoder.
Optimize decoding algorithm to get better performance.
Migrate aacPlus decoder to Windows CE platform.
Performed Unit test, Functional test, System test.

\end{eventlist}

\personal
    {Unit 306, 63 Bank Lane, Kogarah,\newline NSW 2217}
    {+61 422 375 093}
    {thebangnguyen@gmail.com}
    {https://github.com/bangn}
    {https://www.linkedin.com/in/bangtn}

\section{Software Development Skills}

\begin{factlist}

\item{Advance}
    {Ruby, Javascript
    \newline Ruby On Rails, Roda, Sequel, React, Redux
    \newline Postgres, MySQL,
    \newline Rspec, Capybara,
    \newline Agile Development, TDD}

\item{Intermediate}
    {EventMachine, ElasticSearch
    \newline RabitMQ, Xapian, Protobuf
    \newline Docker, AWS}

\item{Beginner}
    {Haskell, Elixir, CSS, Terraform}
\end{factlist}

\section{Education}

\begin{yearlist}

\item[University of Technology]{2012}
    {Master of Information Technology}
    {Sydney, Australia}

\item[Ho Chi Minh City University of Technology]{2008}
    {Bachelor of Computer Science}
    {Ho Chi Minh City, Vietnam}

\end{yearlist}
%:

\section{Awards}

\begin{yearlist}

\item{2004}
    {Academic Achievement Award\newline Scholarship}
    {Ho Chi Minh City University of\newline Technology}

\item{2002}
    {Second Prize in Lam Dong Province Mathematics Competition}
    {Thang Long High School, Lam Dong Province, Vietnam}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Vietnamese}{Native speaker}
\item{English}{Good}
\end{factlist}

\end{document}
