% Wenneker Resume/CV
% LaTeX Template
% Version 1.1 (19/6/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{memoir} % Font and paper size

\input{structure.tex} % Include the file specifying document layout and packages

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\userinformation{ % Set the content that goes into the sidebar of each page
\begin{flushright}
\small % Smaller font size
Bang Nguyen\\ % Your name
\Sep % Some whitespace
\url{thebangnguyen@gmail.com} \\ % Your email address
\url{github.com/bangn} \\ % Your URL
\url{linkedin.com/in/bangtn} \\ % Your URL
0422 375 093 \\ % Your phone number
\end{flushright}
}

%----------------------------------------------------------------------------------------

\begin{document}

\userinformation % Print your information in the left column

\framebreak % End of the first column

%----------------------------------------------------------------------------------------
%	HEADING
%----------------------------------------------------------------------------------------

\cvheading{Bang Nguyen} % Large heading - your name

%----------------------------------------------------------------------------------------
%	ABOUT ME
%----------------------------------------------------------------------------------------

% \aboutme{About Me}{}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\CVSection{Software Development Skills}
\CVItem{Advanced}
{
	\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
		\bluebullet Ruby/Rails & \bluebullet NodeJS & \bluebullet Typescript\\
		\bluebullet React & \bluebullet Docker & \bluebullet Postgres\\
	\end{tabular}
}

\CVItem{Intermediate}
{
	\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
		\bluebullet Kotlin & \bluebullet AWS &  \bluebullet Kafka \\
		\bluebullet ElasticSearch & \bluebullet Terraform
	\end{tabular}
}

\CVItem{Beginner}
{
	\begin{tabular}{p{0.2\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
	\bluebullet Haskell &  \bluebullet Elixir
	\end{tabular}
}

\CVSection{Certificate}
{
	\begin{tabular}{p{0.5\textwidth} p{0.2\textwidth} p{0.2\textwidth}}
	\bluebullet AWS Solution Architect, Associate\\
	\end{tabular}
}

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\CVSection{Experience}

\CVItem{Sept 2021 - March 2024, \textit{Senior Software Engineer}, CashApp /
Block (previously Square)}{
CashApp is a financial platform that offers various services through its app
for iOS and Android. It is catering to tens of millions of monthly active users
(approximately 56 million). I was a member of the team responsible for expanding
Cash App's presence beyond the USA, either by introducing it to new countries
such as Canada or Australia, or by enhancing its features in existing markets
(the United Kingdom).

I was leading the engineers team, collaborating closely with a cross-functional teams
(Product and Design) and various domain specific teams to
successfully deliver the United Kingdon (UK) code-red project.
This initiative enhances the Onboarding and Identity Verification process for
new UK customers and facilitates the re-verification of Identity
for existing UK customers

\begin{itemize}
	\item Leading a team of 5 server engineers and 2 client engineers
	\item Collaborating closely with Product Manager, Product Designer, QA, Data Analysts, Customer Support, and
		operations personnel to orchestrate the intricate series of changes, monitor and
		evaluate success metrics
	\item Facilitating effort to move functionality out of
		CashApp's core monolith transitioning non-US Identity
		Verification process to align with the US IDV
		process and phasing out legacy implementations.
	\item Taking ownership to lead and coordinate Incident responses and mitigate issues
	\item Collaborating and pairing to uplift engineers domain knowledge
	\item Technology used: Kotlin, Java, GRPC, Kafka, MySQL, DynamoDB, Kubernetes, Terraform, Datadog
\end{itemize}
}

\CVItem{Oct 2020 - Sept 2021, \textit{Senior Software Engineer}, Shippit}{
	Shippit provides multi-carrier shipping platform for retailers to
	simplify their deliveries.
	I was involved in wide range of activities at Shippit

\clearpage % Start a new page
\userinformation % Print your information in the left column
\framebreak % End of the first column

\begin{itemize}
	\item Breakdown the Ruby on Rails core monolith application into smaller microservices
	\item Design/develop microservices from proof of concept to production using
		Typescript and Kafka
	\item Integrate carriers API to Shippit core application
	\item Develop tools to empower support agents to resolve customer's request
	\item Mentor junior/internship engineers
	\item Technology used: Ruby/Ruby on Rails, Typescript, Postgres, Kubernetes, Kafka, Docker, AWS
\end{itemize}
}

\CVItem{Oct 2017 - Oct 2020, \textit{Senior Software Engineer}, DiUS}{
The projects I worked on involved but are not limited to the below:
\begin{itemize}
	\item Develop highly available and fault tolerant system that can handle burst-able data being sent 24/7 using a TCP-based protocol (DICOM)
	\begin{itemize}
		\item Dockerize Orthanc server and deploy to AWS ECS with Auto scaling
		\item Develop system to archive DICOM image to S3 and store its metadata
			to ElasticSearch. In peak time, it can handle up to 5GB per minute

		\item Develop UI to allow searching archived data and restore archived
			image to specified location using AWS Step Functions
	\end{itemize}
\end{itemize}

\begin{itemize}
    \item Develop a chatbot to automate tasks that were previously handled by
	    call center agents
	\begin{itemize}
		\item Use Amazon Lex, AWS Lambda, AWS Cloudformation to develop a
			chatbot for NIB which can direct the customer to correct queue in
			the call center.  It helps the business reduce the time it takes for
			a call center agent to serve the customer.
		\item Develop a chat interface using React and embed it into the client
			website.
	\end{itemize}
    \item Develop an application to allow the education agency to manage International Student
	\begin{itemize}
		\item Use React, NodeJS, Ruby to develop a web application to streamline
			how the education agency manage International Student health insurance.
			It was used by education agencies such as IDP to create/purchase/renew
			student's health insurance.
	\end{itemize}
	\item Deploy AWS Control Tower to consolidate all Swinburne University's
		AWS accounts.
	\item Use AWS Lambda and AWS AppFlow to pull data from Salesforce and put
		into the University of Melbourne datalake as part of Virtual Open Day
		program.
    \item Technology used: React, NodeJS, Ruby, Redux, Postgres, ElasticSearch, Docker, AWS
\end{itemize}
}

\CVItem{Sep 2015 - Oct 2017, \textit{Software Engineer}, Digivizer}{
Develop social analytics platform

\clearpage % Start a new page
\userinformation % Print your information in the left column
\framebreak % End of the first column

\begin{itemize}
    \item The platform downloads all customers engagements from their social
    media account (Twitter, Facebook, Instagram) and provides analytics to allow
    them to track their social engagements. Customers who used this platform
    include but are not limited to Microsoft, Lenovo, Deloitte.
    \item Technology used: Ruby, Ruby on Rails, Sequel, React, Redux, Postgres, RabbitMQ,
    Protobuf, ElasticSearch, Docker, AWS, Puppet
\end{itemize}
}

\CVItem{Sep 2014 - Sep 2015, \textit{Software Engineer}, GetUp!}{
Develop and maintain Tijuana Framework
\begin{itemize}
    \item Tijuana Framework is a home grown framework from GetUp! to allow
		campaigners to contact its members via email to communicate on the up
		coming campaign or event.
    \item Technology used: Ruby, Rails, JQuery, MySQL, AWS
\end{itemize}
}

\CVItem{Apr 2008 -- Apr 2014, \textit{Software Engineer/Technical Lead}, Vietnam}{
Work on various projects across Embedded System and Mobile Applications as well
as leading the development
\begin{itemize}
	\item Tech used: Java, C/C++, .NET, MSSQL
\end{itemize}
}

\Sep % Extra whitespace after the end of a major section

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\CVSection{Education}

%------------------------------------------------

\CVItem{2010 - 2011, University of Technology, Sydney}{Master of Information Technology}

%------------------------------------------------

\CVItem{2003 - 2008, Ho Chi Minh City University of Technology, Vietnam}{Bachelor of Computer Science}

%------------------------------------------------

\end{document}
