\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Bang Nguyen}

\section{Work experience}

\begin{eventlist}

\item{September 2015 -- Present}
     {DIGIVIZER, Sydney}
     {Ruby Developer}

Develop social analytics platform that allows users to discover
what matter to them on social platforms (Twitter, Facebook, Instagram).
This could help business owners find a relevant customers
to their business and provide them with insight\newline analytics.

\item{September 2014 -- September 2015}
     {GET UP!, Sydney}
     {Fullstack Software Developer}

Develop and maintain Tijuana Framework which is a CMS
used by campaigners to blast out emails to GetUp's members.
Work in all layers of application stack from cloud infrastructure (AWS)
to database (MySQL) to application code (Ruby on Rails)
to user interface(CSS, BootStrap, SASS,\newline Javascript, JQuery).
Participate in pairing and code review.

\item{July 2013 -- April 2014}
     {SIMPSON STRONGTIE, Vietnam}
     {Technical Leader}

Design, develop and maintain applications to\newline automate works which were previously done by construction engineers.
Design, develop and test new features of Component Solutions Suite to gather all scattered databases to one centric database.
Fix bugs, provide ongoing support to legacy\newline system.
Manage team and provide estimation to development tasks.

\item{September 2012 -- June 2013}
     {GLOBAL CYBERSOFT, Vietnam}
     {Lead Engineer}

Develop and maintain Set Up Box's applications.
Provide solutions to improve Set Up Box's performance.

\item{March 2010 -- October 2010}
     {FPT SOFTWARE, Vietnam}
     {Windows Phone Developer}

Maintain Windows Phone mobile applications.
Fix bugs reported by QA team.
Migrate applications to other mobile models.

\item{September 2009 -- February 2010}
     {WE ARE ENGINEERING, Vietnam}
     {Android Developer}

Design, develop and maintain Android game named Cubic Gomoku.
Design, develop Youtube-like program using Youtube's API.

\end{eventlist}

\personal
    {Unit 306, 63 Bank Lane, Kogarah,\newline NSW 2217}
    {+61 422 375 093}
    {thebangnguyen@gmail.com}
    {https://github.com/bangn}
    {https://www.linkedin.com/in/bangtn}
        
\section{Education}

\begin{yearlist}

\item[University of Technology]{2012}
     {Master of Information Technology}
     {Sydney, Australia}

\item[Ho Chi Minh City University of Technology]{2008}
     {Bachelor of Computer Science}
     {Ho Chi Minh City, Vietnam}

\end{yearlist}
%:

\section{Awards}

\begin{yearlist}

\item{2004}
     {Academic Achievement Award\newline Scholarship}
     {Ho Chi Minh City University of\newline Technology}

\item{2002}
     {Second Prize in Lam Dong Province Mathematics Competition}
     {Thang Long High School, Lam Dong Province, Vietnam}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Vietnamese}{Native speaker}
\item{English}{Good}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Advance}
     {Ruby, C/C++, Javascript,
     Ruby On Rails, Roda, Sequel, React, Redux, JQuery,
     RabitMQ, Xapian, Protobuf,
     Postgres, MySQL,
     Rspec, Capybara,
     Agile Development, TDD}

\item{Intermediate}
     {Java , PhantomJS, Jasmine}

\item{Beginner}
     {Elixir, CSS (Bootstrap, SASS)}
\end{factlist}

\end{document}
